Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-17 writeup/rocha_etal.tex
Small edits in conclusion

Internal tide energy flux does not show a seasonal modulation \citep[e.g.,][]{alford2003},
hence one expects a strong seasonality in the near-surface
expression of internal tides and
higher frequency IGWs if the near-surface stratification varies strongly.
Windy near-inertial wave (NIW) generation is bursty and peaks in early winter, but
NIW energy appears to have similar energy level in October and April
\citep{alford_etal2016}.
While NIWs are generated at large scales, mesoscale turbulence can
refract and disperse those waves in few inertial periods, thereby generating
submesoscale (10-100 km) near-inertial waves \citep{alford_etal2016}. But in our
simulations the inertia-gravity-wave seasonality in submesoscale surface KE and SSH
variance is mostly accounted for
by higher frequency waves  (Figure \ref{fig4}a-b), likely because submesoscale
NIWs quickly propagate into the interior and weakly project onto SSH.

In the context of the SWOT mission, our results suggest that if one is interested
only in the geostrophic flow, so that surface velocity can be diagnosed
from SSH, then the noise-to-signal ratio will have a strong seasonality.
An important caveat is that this study focuses on a single patch of ocean in the
vicinity of the Kuroshio Extension. This may be typical of a mesoscale-rich
subtropical region, but it is unlikely to be
representative of other regions such as low-eddy-kinetic-energy eastern boundary currents
and the middle of the subtropical gyre.  We plan to report on the geographic variability of submesoscale
seasonality in a future study.

>>>>

Internal tide energy flux does not show a seasonal modulation \citep[e.g.,][]{alford2003},
hence one expects a strong seasonality in the near-surface
expression of internal tides and
higher frequency IGWs if the near-surface stratification varies strongly.
Windy near-inertial wave (NIW) generation is bursty and peaks in early winter, but
NIW energy appears to have similar energy level in October and April
\citep{alford_etal2016}.
While NIWs are generated at large scales, mesoscale turbulence can
refract and disperse those waves in few inertial periods, thereby generating
submesoscale (10-100 km) near-inertial waves \citep[][and references therein]{alford_etal2016}.
But in our simulations the inertia-gravity-wave seasonality in submesoscale surface KE and SSH
variance is mostly accounted for
by higher frequency waves  (Figure \ref{fig4}a-b), likely because submesoscale
NIWs quickly propagate into the interior and weakly project onto SSH.

In the context of the SWOT mission, our results suggest that if one is interested
only in the geostrophic flow, so that surface velocity can be diagnosed
from SSH, then the noise-to-signal ratio will have a strong seasonality owing
to the presence of incoherent IGWs.
An important caveat is that the Kuroshio Extension may be typical of a mesoscale-rich
subtropical regions, but it is unlikely to be
representative of other regions such as low-eddy-kinetic-energy eastern boundary
currents.  We plan to report on the geographic variability of submesoscale
seasonality in a future study.
